---
title: "In Class Exercises - Sorting and Filtering"
author: "Nikola Misetic"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

## Setup and Loading Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the packages we'll need
# Remember, think of this like packing for our trip
# (We don't take the whole closet, only what we need)
library(tidyverse)
library(lubridate)

```

Run this line below load the data for this assignment. It will load a dataframe called "impeach," containing U.S. House Democrats and whether they supported the first impeachment of Pres. Trump, along with when they announced such support.

```{r}

impeach <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRh8d5JaDqBtByzNw2JZF3idaACobDhhk-p7chJoktA0HawELHFOvjQOqCpzGA4MGONvPlR7GASqW-K/pub?gid=1765341510&single=true&output=csv")


```

Let's see what we have:

```{r}

impeach


```

## Exercise Questions

*For the questions below, write your R code to return the requested records in the code chunk provided.*

1)  The column "for_impeachment" indicates whether the member has publicly called for an impeachment inquiry. Filter to return only the ones where the answer is NO.

```{r}

impeach %>% 
  filter(for_impeachment=="NO")

# I selected the impeach table, created a pipe, and filtered for "NO" votes on impeachment



```

2)  Filter to return only results where a member is both against impeachment, and comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column).

```{r}

impeach %>% 
  filter(for_impeachment=="NO") %>% 
  filter(p16winningparty=="R")

# Used the same code for question 1, added another pipe to filter by Trump-won districts

```

3)  Filter for only results where a member is against impeachment, comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column), and also comes from a district that Mitt Romney won in 2012 ("p12winningparty").

```{r}

impeach %>% 
  filter(for_impeachment=="NO") %>% 
  filter(p16winningparty=="R") %>% 
  filter(p12winningparty=="R")

# Used the same code for question 2, added another pipe to filter by Romney-won districts

```

4)  Filter for only results from September 2019 where a member is a YES for impeachment.

```{r}

impeach %>% 
  filter(date_month==9) %>% 
  filter(date_year==2019) %>%
  filter(for_impeachment=="YES")

# I created a new pipe, filtered by month (September/9), year (2019), and finally yes votes

```

5)  Filter for only results where a member is a YES for impeachment and is from a district where Clinton won more than 70 percent of the vote in 2016 (found in column "clinton_percent").

```{r}

impeach %>%
  filter(for_impeachment=="YES") %>% 
  filter(clinton_percent>70)

# I created a new pipe, filtered by Yes votes, and then filtered for Clinton district victories greater 70%

```

6)  Sort the entire dataframe based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.

```{r}

impeach %>% 
  arrange(pct_bachelors)

# I created a new impeach pipe with an arrange function, which arranges the data from lowest to highest by default


```

7)  Sort the just those who are NO on impeachment based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.

```{r}





```

8)  Sort the just those who are NO on impeachment based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.

Then filter those records by only those whose bachelor's percentage is below the national average (found in the "pct_bachelors_compared_to_national" column).

```{r}






```

9)  Filter for only members from New Jersey who are NO on impeachment.

```{r}





```

10) Filter for those who were YES on impeachment, with a declared date prior to 2019. So only those with dates before 2019. Then sort those so that the highest Clinton vote percentages are at the top.

```{r}





```
